Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-01-04 paper/notes.tex
WIP

\subsubsection{Rotation experiments)}

@@

In the basic, $N=56$ wild type simulation, $D$ seems to need to be close to
0.02. Unfortunately, the simulation is unstable for $\delta t=0.0001$ and
$d=0.015$. Having fixed a bug which prevented me from reducing $d$ very much,
and having implemented fixed seed random numbers for repeatable sims,
I can now try to determine if a smaller $d$ will help the simujlation compute,
though note that as $d$ is reduced, so $\delta t$ must be reduced, leading to
longer simulation computations.

@@

I've already implemented systems in which $a$ is bounded. Simplest is probably
best - a piecewise linear transfer function on $a$. Thus, I've added the code
to rd_barrel.h to compute a transformed version of $a$ called $\bar{a}$ and
use this in the computation. It mitigates the instabilities without
making much change to the operation of the model. It adds an additional
parameter to the model, $a_{max}$, which I've set to 0.5 by default.

>>>>

\subsubsection{Rotation experiments}

@@

In the basic, $N=56$ wild type simulation, $D$ seems to need to be close to
0.02. Unfortunately, the simulation is unstable for $\delta t=0.0001$ and
$d=0.015$. Having fixed a bug which prevented me from reducing $d$ very much,
and having implemented fixed seed random numbers for repeatable sims,
I can now try to determine if a smaller $d$ will help the simulation compute,
though note that as $d$ is reduced, so $\delta t$ must be reduced, leading to
longer simulation computations.

@@

I've already implemented systems in which $a$ is bounded. Simplest is probably
best - a piecewise linear transfer function on $a$. Thus, I've added the code
to rd\_barrel.h to compute a transformed version of $a$ called $\bar{a}$ and
use this in the computation. It mitigates the instabilities without
making much change to the operation of the model. It adds an additional
parameter to the model, $a_{max}$, which I've set to 0.5 by default.
